---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
1. Load the data

```{r,echo=TRUE}
#setwd(dirname(parent.frame(2)$ofile))
df<-read.csv("activity//activity.csv",header=TRUE,na.strings="NA")
df$date<-as.Date(df$date,"%Y-%m-%d")
```

## What is mean total number of steps taken per day?
Calculate the total number of steps taken per day  

```{r,echo=TRUE,message=FALSE}
library (plyr)
library(dplyr)
library(tidyr)
```

```{r}
# opcion1) steps_per_day<-df[,-3]%>% group_by(date) %>% summarise_each(funs(mean(.,na.rm=TRUE)))
# opcion2) steps_taken_per_day <- aggregate(steps ~ date, tidy, sum)
#colnames(steps_taken_per_day) <- c("date", "steps")
steps_per_day <- ddply(df[,-3], c("date"), summarise,
                       sum = sum(steps, na.rm=TRUE)
                       )

```

Make a histogram of the total number of steps taken each day  

```{r}
hist(steps_per_day$sum,breaks=30,
     main="Steps per day",xlab="Number of steps per day",ylab="Frequency")
```

Calculate and report the mean and median of the total number of steps taken per day

```{r}
mean_per_day<-mean(steps_per_day$sum)
median_per_day<-median(steps_per_day$sum)

```

The mean is `r mean_per_day` and the median is `r median_per_day` steps per day.
 
 


## What is the average daily activity pattern?

Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
# When using the aggregate() function, the by variables must be in a list (even if there is only one). The function can be built-in or user provided.
interval_steps<-aggregate(df$steps, by=list(df$interval), FUN=mean, na.rm=TRUE)
colnames(interval_steps)<-c("Interval", "Mean_steps")

library(ggplot2)
ggplot(data=interval_steps, aes(x=Interval,y=Mean_steps)) + 
    geom_line() + 
    ylab("Mean steps") + 
    xlab("5 min Intervals")
```
Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
max_interval<-interval_steps[which.max(interval_steps$Mean_steps),] $Interval
```

The `r max_interval` interval has the max average of steps.  


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
