---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
1. Load the data

```{r,echo=TRUE}
#setwd(dirname(parent.frame(2)$ofile))
df<-read.csv("activity//activity.csv",header=TRUE,na.strings="NA")
df$date<-as.Date(df$date,"%Y-%m-%d")
```

## What is mean total number of steps taken per day?
Calculate the total number of steps taken per day  

```{r,echo=TRUE,message=FALSE}
library (plyr)
library(dplyr)
library(tidyr)
```

```{r}
# opcion1) steps_per_day<-df[,-3]%>% group_by(date) %>% summarise_each(funs(mean(.,na.rm=TRUE)))
# opcion2) steps_taken_per_day <- aggregate(steps ~ date, tidy, sum)
#colnames(steps_taken_per_day) <- c("date", "steps")
steps_per_day <- ddply(df[,-3], c("date"), summarise,
                       sum = sum(steps, na.rm=TRUE)
                       )

```

Make a histogram of the total number of steps taken each day  

```{r}
hist(steps_per_day$sum,breaks=30,
     main="Steps per day",xlab="Number of steps per day",ylab="Frequency")
```

Calculate and report the mean and median of the total number of steps taken per day

```{r}
mean_per_day<-mean(steps_per_day$sum)
median_per_day<-median(steps_per_day$sum)

```

The mean is `r mean_per_day` and the median is `r median_per_day` steps per day.
 
 


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
